### 2018-10-30 Chapters/Chapter3.tex
change title

\begin{equation}
\label{Jij2}
J_{ij}(t) = \sum_{n} 2t_0^2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
\end{equation}

For $\omega>>U$ we can truncate \ref{Jij2} to the three smallest values of $n$, i.e. $n=0, \pm 1$. We can also use that $\alpha_{ij} << 1$ because $\alpha_{ij}$ is proportional to $\vec{A}$ which is proportional to $\omega^{-1}$. Therefore we can use $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:

\begin{equation}
\label{Jij3}
J_{ij} \approx 2t_0^2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right) = J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
\end{equation}

@@

From here we can see that if we take the same approximation as in \ref{Jij3} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.

>>>>

\begin{equation}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx \sum_{n} 2 \frac{\mathcal{J}_n(\alpha_{ij})^2}{\text{U}+n\omega}
\end{equation}

For $\omega>>U$ we can truncate this to the three smallest values of $n$, i.e. $n=0, \pm 1$. We can also use that $\alpha_{ij} << 1$ because $\alpha_{ij}$ is proportional to $\vec{A}$ which is proportional to $\omega^{-1}$. Therefore we can use $J_n(x) \approx x^n \text{ for } n>0 \text{ and } x << 1$ to obtain:

\begin{equation}
\label{MFactorApprox}
\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t) \approx 2 \left(\frac{\alpha_{ij}^2}{\text{U}+\omega} +\frac{1}{\text{U}} +\frac{\alpha_{ij}^2}{\text{U}-\omega} \right)
\end{equation}

And the exchange interaction coupling becomes:

\begin{equation}
\label{Jij2}
J_{ij} \approx J_{ij}^0 + 2t_0^2 \alpha_{ij}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
\end{equation}

@@

From here we can see that if we take the same approximation as in \ref{Jij2} we will obtain the same form of exchange interaction for circular polarized light ($\lambda=\pm1$) \ref{JijCPSQUARE} with possibly a different lattice constant $a$.

### 2018-10-30 Chapters/SGraphene.tex
change title

In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. However, if inversion symmetry is broken by i.e. an external electric field in the $\hat{z}$ direction, a Rashba spin orbit interaction term is allowed between nearest neighbors. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model:

@@

This describes a type of anisotropic exchange interaction. Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the time dependence will not be the same, since the structure terms $\alpha_{ij}$ will change for next-nearest neighbors $i$ and $j$.

>>>>

In graphene time reversal symmetry and inversion symmetry allow only next-nearest neighbor spin orbit coupling, which is known as intrinsic spin orbit coupling. However, if inversion symmetry is broken by i.e. an external electric field in the $\hat{z}$ direction, a Rashba spin orbit interaction term is allowed between nearest neighbors. In these circumstances the system can be modeled by the Kane-Mele-Hubbard model \cite{Laubach2014}:

@@

This describes a type of anisotropic exchange interaction. Notice that although the factor $\mathcal{M}(\alpha_{ij}, \text{U}, \omega, t)$ that renormalizes the interaction coupling in presence of the electric field has the same form as in \ref{JijHSOI} and \ref{DijHSOI}, the renormalization will not be the same, since the structure terms $\alpha_{ij}$ will differ from those in a nearest neighbor interaction. For example, if we take the time independent approximation \ref{MFactorApprox}, then the exchange interaction will be:

\begin{align*}
J_{ij} = J_{ij}^0 + t_0^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
\end{align*}

Where $\mathcal{E} = \frac{eaE_0}{\omega}$. Whereas the anisotropic exchange coupling will be:

\begin{align*}
H_{ij} = H_{ij}^0 + 3 \Delta^2 \mathcal{E}^2 \left( \frac{1}{\text{U}+\omega} + \frac{1}{\text{U}-\omega} \right)
\end{align*}

Where $H_{ij}^0 = \frac{2\Delta^2}{\text{U}}$ is the anisotropic exchange coupling in the absence of electromagnetic field, and the factor $3$ arises from the structure factor $\alpha_{ij}$ being $\sqrt{3}$ times larger for next nearest neighbors in a honeycomb lattice.
